Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 4 updates

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
\hline
$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
\hline
$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
\hline
$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
\hline
$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
\hline
$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
\hline
\end{tabular}
\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a \textbf{faculae}, according to Eq.~\ref{eq:RV:correction}. All the variables, except the intercept when the independent variable is SN median RV, are statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
\label{table:faculae.test}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
\hline
$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
\hline
$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
\hline
$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
\hline
$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
\hline
$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
\hline
\end{tabular}
\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated  RVs from spurious variations caused by a facula. All the variables, except the intercept when the response variable is SN median RV, are statistically significant to explain spurious variations in RV's caused by a facula. The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.}
\label{table:faculae.test}
\end{table}
